---
title: "Basic Problems on FUNCTION"
author: "Gunjan Shah"
date: "March 9, 2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## I am posting several basic problem set with their answers and explaination.

#Problem 1
```{r}
cube <- function(x, n) {
        x^3
}
# Now what will be the answer for cube(3)?
cube(3)
```
## Although cube is a function of variable x and n and nowhere the variable n is called, the function will not generate any error as it is not necessary to have all the variables to be used. 

#Problem2
```{r}
x <- 1:10
if(x > 5) {
        x <- 0
}
# What will be the warning here?
```
# Here x is a vector of length 10 and 'if' condition can only test a single logical statement.

#Problem3
```{r}
f <- function(x) {
        g <- function(y) {
                y + z
        }
        z <- 4
        x + g(x)
}
z<-10 #Notice that I did assign the value for z in the function f
f(3)
# What will be the value of f(3)? 
# So you need to think what will be the value of z, 4 or 10?
```
# R uses the method of lexical scoping(static scoping), so the value of z here will be the value that we assigned in the parent function. Although if you want to assign any value strictly then you can define it as a global value initially.

#Problem4
```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
y
# What value will be printed for y ?
```
# Here x is a vector of length 1. The if statement hence will be tested logically and value will be assigned in the variable y accordingly.

#Problem5
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
# Which symbol in the above function is a free variable?
```
# This is again a basic question to assess your basic knowledge regarding the environment of R. Read more on this topic and try to justify that why f is the free variable here.

#Problem6
#What is an environment in R?
#A collection of symbol/Pair values.

#Problem7
#The R language uses what type of scoping rule for resolving free variables?
#Lexical scoping or static scoping. Do try to read the difference between lexical vs dynamic scoping.

#Problem8
#How are free variables in R functions resolved?
#The values of free variables are searched for in the environment in which the function was defined

#Problem9
#What is one of the consequences of the scoping rules used in R?
#All objects must be stored in memory

#Problem10
#In R, what is the parent frame?
#It is the environment in which a function was called.